Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-04 paper/main.tex
Updates

\begin{figure}[t!]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\begin{Verbatim}[fontsize=\footnotesize]
You are an expert in Social Science. Following
are the descriptions of two variables:

<A>: {description of variable A}
<B>: {description of variable B}

Which of the following two options is the most 
likely causal direction between these variables:

1. <A> causes <B>
2. <B> causes <A>

Return a single letter answer between the 
choices above; Do not provide any reasoning 
in the answer; Do not add any text formatting 
to the answer.
		\end{Verbatim}
	\caption{Prompt used for the LLM}
	\end{subfigure}
	\begin{subfigure}{0.5 \textwidth}
		\begin{Verbatim}[fontsize=\footnotesize]
Age: The age of a person
Workclass: The workplace where the person is 
     employed such as Private industry, 
     or self employed
Education: The highest level of education the 
     person has finished
MaritalStatus: The marital status of the person
Occupation: The kind of job the person does. 
     For example, sales, craft repair, clerical.
Relationship: The relationship status of 
     the person
Race: The ethnicity of the person
Sex: The sex or gender of the person
HoursPerWeek: The number of hours per week the 
     person works
NativeCountry: The native country of the person
Income: The income i.e. amount of money the 
     person makes
		\end{Verbatim}
	\caption{Variable descriptions used for prompting the LLM}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[scale=0.3]{../code/fig5/llm_adult.png}
		\caption{The learned DAG}
	\end{subfigure}
\end{figure}

\section{Conclusions}
\begin{itemize}
	\item As researchers prefer to anyways build models by hand, this is like a companion tool to help them in deciding the method.
	\item Solves all the $ 3 $ issues outlined in the introduction.
	\item Compared to other expert knowledge specification methods, users don't need to guess what information then need to provide as exact questions are asked. Also enables us to ask an LLM for it.
\end{itemize}

@@

\newpage
\bibliography{references}
\end{document}

>>>>

\begin{figure}[t!]
	\centering
	\includegraphics[scale=0.3]{../code/fig5/llm_adult.png}
	\caption{The learned DAG}
\end{figure}

\section{Conclusions}
Points:
\begin{itemize}
	\item As researchers prefer to anyways build models by hand, this is like a companion tool to help them in deciding the method.
	\item Solves all the $ 3 $ issues outlined in the introduction.
	\item Compared to other expert knowledge specification methods, users don't need to guess what information then need to provide as exact questions are asked. Also enables us to ask an LLM for it.
\end{itemize}

@@

\bibliography{references}

\newpage

\include{appendix}
\end{document}
